---
title: "Evaluating the social, economic, and ecological costs and benefits of levee infrastructure within the Delta"
format: dashboard
---

```{r load libraries}
#| include: false

library(dplyr)
library(sf)
library(ggplot2)
library(readr)
library(leaflet)
library(mapview)
library(leafpop)
library(here)
library(palmerpenguins)

```

```{r read data}
levee_area <- read_sf(here("mock_data", "levees_shapefiles", "fixedLevees.shp"))

rand_mock <- read_csv(here("mock_data", "mock_rand_data.csv"))

levee_area_data <- levee_area %>% 
  mutate(island_tract = paste0("island_", 1:139)) %>% 
  left_join(rand_mock, by = "island_tract")

```


# Reulsts

## Column 1 {width=30%}


```{r}
#| content: valuebox
#| title: "Total Penguins"

list(
  icon = "hash",
  color = "warning",
  value = nrow(penguins)
)
```



```{r}
#| content: valuebox
#| title: "Penguin Species"

list(
  icon = "feather",
  color = "light",
  value = length(unique(penguins$species)))
```


## Column 2 {width=70%}

::: {.card title="About Palmer Station" height=25%}
[Palmer Station](https://pallter.marine.rutgers.edu/) is a site part of the Long-Term Ecological Research (LTER) Network. It is one of the three United States research stations located in Antarctica. 

It is also where the data from the [Palmer Penguins](https://allisonhorst.github.io/palmerpenguins/) R package was collected. The penguin data was collected and made available by [Dr. Kristen Gorman](https://www.uaf.edu/cfos/people/faculty/detail/kristen-gorman.php).


:::



```{r}


```


# Data {orientation="rows"}

## Row 1 {height="10%"}

::: {.card}
Levees are critical to life in the Delta, but management decisions on funding for upkeep and improvement are not fully informed by available data.
:::


## Row 2 {height="70%"}

### Column 1

```{r}
#| title: Penguin Scatterplot


ggplot(data = penguins, aes(x = flipper_length_mm, y = body_mass_g)) +
    geom_point(aes(color = species)) +
    scale_color_manual(values = c(
        "Adelie" = "purple2",
        "Chinstrap" = "orange",
        "Gentoo" = "cyan4"
    )) +
    labs(
        title = NULL,
        x = "Flipper Length (mm)",
        y = "Body Mass (g)",
        color = "Species"
    ) +
    theme_minimal()
```


### Column 2



```{r}
#| title: Bill Depth Distribution of Chinstrap

penguins %>%
    filter(species == "Chinstrap") %>%
    ggplot(aes(x = bill_depth_mm)) +
    geom_histogram(fill = "orange") +
    labs(title = NULL,
         x = "Bill Depth (mm)",
         y = NULL) +
    theme_minimal()
```



```{r}
#| title: Penguin Species on Biscoe Island

# subsetted penguins data frame
biscoe_sp <- penguins %>% 
    filter(island == "Biscoe") %>% 
    group_by(species) %>% 
    summarize(count = n())
    
# bar plot 
ggplot(data = biscoe_sp, aes(x = species, y = count)) +
    geom_col(aes(fill = species)) +
    scale_fill_manual(values = c(
        "Adelie" = "purple2",
        "Gentoo" = "cyan4"
    )) +
    labs(title = NULL,
         x = NULL,
         y = "Number of species",
         fill = "Species") +
    theme_minimal() 
```




