---
title: "Mapping Levee Islands"
format: html
---

## About this script
Here we will look into different ways of visualizing the levee island with the data layers of the RAND model using a "mock" data set.

## Set up

```{r}
library(dplyr)
library(sf)
library(ggplot2)
library(readr)
library(leaflet)
library(mapview)
library(leafpop)
library(here)

```


## Read data

**Spatial Data: Levee islands**

These shapefiles come from the swg-23-infrastructure repository unde clean-data

```{r}
levee_area <- read_sf(here("mock_data", "levees_shapefiles", "fixedLevees.shp"))

plot(levee_area$geometry)

head(levee_area)

```

**Mock Data: RAND model output**

```{r}
rand_mock <- read_csv(here("mock_data", "mock_rand_data.csv"))
```


## Joining spatial data with model mock data
```{r}
levee_area_data <- levee_area %>% 
  mutate(island_tract = paste0("island_", 1:139)) %>% 
  left_join(rand_mock, by = "island_tract")
```



## Plotting with `mapview`
```{r}
mapview(levee_area_data, zcol = c("risk_scaled_percent",
                                  "prob_flood",
                                  "water_quality"),
        popup = popupTable(
    levee_area_data,
    zcol = c(
      "risk_scaled_percent",
      "prob_flood",
      "water_quality"
      )
    )
    )
```

Next steps
- Plot different layers
- Create a dashboard with map + Explanation of RNAD layers



## Leaflet basemap

```{r}
leaflet() %>% 
    addTiles(
        urlTemplate = "https://api.mapbox.com/styles/v1/moowill/cki3zbj5o4k4b19qlq98amqia/tiles/{z}/{x}/{y}?access_token=pk.eyJ1IjoibW9vd2lsbCIsImEiOiJja2kzejloOHkxdzNtMnhxcTAwY3Zqa25zIn0.VCsBGYnJr6Z7A7XnD157cg",
        attribution = 'Maps by <a href="http://www.mapbox.com/">Mapbox</a>'
    )  %>% 
    setView(lat=38.1, lng=-121.8, zoom=10)
    # addMarkers(data = points(), group="Location Pin")
```



